High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 introduction.tex
Typo

In spite of the impressive scale of the ATLAS distributed computing system --
in the number of tasks executed, the number of core hours utilized, and the
number of distributed sites utilized,  demand for computing systems will soon
significantly outstrip current and projected supply.   The data volumes that
will need analyzing in LHC-Run 3 ($\approx$ 2022) and the high-luminosity
era (Run 4) will increase by factors of 10--100 compared to the current phase
(Run 2). There are multiple levels at which this problem needs to be
addressed: the utilization of emerging parallel architectures (e.g.,
platforms); algorithmic and advances in analytical methods (e.g., use of
Machine Learning); and the ability to exploit different platforms (e.g.,
clouds and supercomputers).

>>>>

In spite of the impressive scale of the ATLAS distributed computing system --
in the number of tasks executed, the number of core hours utilized, and the
number of distributed sites utilized,  demand for computing systems will soon
significantly outstrip current and projected supply.   The data volumes that
will need analyzing in LHC-Run 3 ($\approx$2022) and the high-luminosity
era (Run 4) will increase by factors of 10--100 compared to the current phase
(Run 2). There are multiple levels at which this problem needs to be
addressed: the utilization of emerging parallel architectures (e.g.,
platforms); algorithmic and advances in analytical methods (e.g., use of
Machine Learning); and the ability to exploit different platforms (e.g.,
clouds and supercomputers).
